I was born in a small town in mid-inland-China. My grandpa, Shouli Sun, 
is the first man to educate me. He was so kind and patient, and his education 
was so successful that I could read 2,000 Chinese characters at the age of 3, 
when my grandpa passed away. With a good start, I became used to being the 
first place in a variety of exams throughout elementary school, middle school, 
and high school. Peking university seemed to be the end of my personal 
progress in education, until I learnt that there is a way to continue my 
graduate study abroad, more specifically, in the US. So I would like to 
thank Dr. Fu, Mr. Qiu and Mr. Yang for providing such information and 
suggestions as my roommates at that time.

The beginning of my graduate school experience was not 
so wonderful. I got lost among the labs of the ECE department since there are 
too many directions and categories of research. Finally, I found out what
I am really interested in after taking the lectures by my advisor, 
Prof. Priyank Kalla. He led the way towards designing a beautiful and powerful
algorithm and applying it to the ``mission impossible" -- verifying
a large circuit with 100\% fault coverage. I would like to thank him for
his valuable guidance, magnificent inspirations, and of course, his generous 
financial support that allow me to carry out my research. Meanwhile, I would 
like to thank four professors serving as my supervisory committee members, 
for their kind help in assisting my research and coursework, as well as the 
review of this dissertation.

At last, I want to say thank you to the most important people in my life.
My parents, Feng Sun and Qinghua Zhang, dedicate themselves to raising me
in a happy family for 26 years. They also keep motivating me to pursue higher 
education and more achievements in schools and universities. My dear wife,
Dr. Huizhong Li, has been my greatest support in the past 10 years. It is our 
precious time working together towards the same goal in the same university, and 
I will remember our life full of sweets and bitters in Salt Lake
City forever.
